%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% based on LaTeX Template: Curriculum Vitae
%
% Source: http://www.howtotex.com/
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[paper=a4,fontsize=11pt]{scrartcl} % KOMA-article class
							
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm}     % Math packages
\usepackage{graphicx}                    % Enable pdflatex
\usepackage[svgnames]{xcolor}            % Colors by their 'svgnames'
\usepackage[left=2cm, right=1.4cm, top=1cm, bottom=1cm]{geometry}
\usepackage{hyperref}
	\textheight=700px                    % Saving trees ;-)
\usepackage{url}
\usepackage{titlesec}
\hyphenpenalty=10000
\hbadness=10000
\frenchspacing              % Better looking spacings after periods
\pagestyle{empty}           % No pagenumbers/headers/footers

%%% Custom sectioning (sectsty package)
%%% ------------------------------------------------------------
\usepackage{sectsty}

\sectionfont{%			            % Change font of \section command
	\usefont{OT1}{phv}{b}{n}%		% bch-b-n: CharterBT-Bold font
	\sectionrule{0pt}{0pt}{-5pt}{3pt}}

%%% Macros
%%% ------------------------------------------------------------
\newlength{\spacebox}
\settowidth{\spacebox}{8888888888}			% Box to align text
\newcommand{\sepspace}{\vspace*{1em}}		% Vertical space macro

\newcommand{\MyName}[2]{ % Name
	\Huge \usefont{OT1}{phv}{b}{n} \hfill #1
	\par \normalsize \normalfont
	\usefont{OT1}{phv}{b}{n} \hfill latest version:\href{http://joelhutton.me/cv.pdf}{joelhutton.me/cv.pdf}
	\normalsize \normalfont
	}
	
\newcommand{\NewPart}[1]{\section*{\uppercase{#1}}}

\newcommand{\PersonalEntry}[2]{
	\noindent\hangindent=2em\hangafter=0 % Indentation
	\parbox{\spacebox}{        % Box to align text
	\textit{#1}}               % Entry name (birth, address, etc.)
	#2 \small \par \normalsize}    % Entry value

\newcommand{\SkillsEntry}[2]{      % Same as \PersonalEntry
	\noindent \textbf{#1} \hfill      % Study
	\par
	\noindent\hangindent=5em\hangafter=0 \small #2 % Description
	\small \par \normalsize}
	
\newcommand{\OccupationEntry}[4]{
	\noindent \textbf{#1} \hfill                         % Study
		\parbox{6em}{%
		#2} \small \par \normalsize                   % Duration
	\noindent \textit{#3} \small \par \normalsize         % School
	\noindent\hangindent=2em\hangafter=0 \small #4 % Description
	\small \par \normalsize}
\begin{document}

\MyName{Joel Hutton}

%%% Personal details
%%% ------------------------------------------------------------
\NewPart{Personal details}{}

\PersonalEntry{Address}{32 Pearl Close, Cambridge, CB4 1QD}
\PersonalEntry{Phone}{\href{tel:+447365536032}{+447365536032}}
\PersonalEntry{Email}{\href{mailto:jah1809@gmail.com}{jah1809@gmail.com}}

%%% Education
%%% ------------------------------------------------------------
\NewPart{Education}{}

\OccupationEntry{BEng. Computer Science and Electronics (1st) }
	{2013-2017}
	{University of Edinburgh}
	{
		NEC semiconductor prize for excellence in first year
		engineering.
	}
\OccupationEntry{Scottish Highers }
	{2008-2013}
	{Balfron High School}
	{
		English: \textbf{A},
		Maths: \textbf{A},
		Physics: \textbf{A},
		Chemistry: \textbf{A},
		Biology: \textbf{A}
	}

%%% Work experience
%%% ------------------------------------------------------------
\NewPart{Employment history}{}

\OccupationEntry{Firmware Engineer - Trusted Firmware}
	{2017-present}
	{Arm, Full-time}
	{Firmware engineering in C, Arm v8-A assembly and Arm v7-A assembly.
		Tools in C. Owner of continuous integration in Shell and Python.
		Produced Spectre mitigations in Trusted Firmware, significant
		memory optimisations.
	}
\OccupationEntry{Software Engineer}
	{2018}
	{Arm, Full-time secondment}
	{
	Researching Mixed Reality technologies, developing test applications
	in Unity.
		}
\OccupationEntry{Tutor}
	{2015-2017}
	{Self-employed, part-time}
	{Tutoring of high school students in Maths, Physics and Computer
	Science while studying}
\OccupationEntry{Software Engineer}
	{2014}
	{Interface3/Tigerface Games, Full-time}
	{Produced a series of multi platform games for autistic children using
	the Unity game engine, programming in C\#. Acted as the core developer,
	working alongside a graphic designer. Produced four games targeting
	mobile platforms. Other short term projects included an app for Mental
	Health Scotland, (SAMH) using HTML, CSS, JavaScript etc.
	}
\OccupationEntry{Software Engineer}
	{2014}
	{Chamberlain McBain, Full-time}
	{Front-end and back-end web development in PHP, HTML, CSS, Javascript, SQL etc.}
%%% Skills
%%% ------------------------------------------------------------
\NewPart{Skills}{}
\SkillsEntry{Programming languages}
	{C, Python, Shell, Arm v8-A assembly, Arm v7-A assembly}
\SkillsEntry{Software development}
	{Git, Gerrit, Jenkins, Docker, CBMC formal verification}
\NewPart{About me}{
			In my free time, I enjoy climbing, motorbikes and squash.
		}

\end{document}
